IMD and calls

### 2022-02-27 output/imd_report.Rmd
n8 webinar and imd stuff

cheshire_calls <- calls %>% filter(lsoa %in% unique(cheshire_lsoas$LSOA11NM))

@@

weekly_count_by_lsoa <- cheshire_calls %>% 
   mutate(inc_wk = as_date(yearweek(incident_date_time))) %>%   
   group_by(lsoa, inc_wk) %>% count() %>% 
  left_join(lsoa_filler, .) %>%
    mutate(n = replace_na(n, 0)) %>% 
    left_join(., cheshire_lsoas %>% st_drop_geometry(), by = c("lsoa" = "LSOA11NM")) %>% 
  filter(!is.na(index_of_multiple_deprivation_imd_decile)) # check why NAs

@@

@@

We can zoom into the time period immediately preceding and following the lockdown period, however we see no real shift in where the calls were coming from in terms of the levels of deprivation in these areas.

@@

# Plot
ggplot(thing %>% filter(inc_wk > as.Date("2019-10-10")), 
       aes(x=inc_wk, y=percentage, fill=as.factor(index_of_multiple_deprivation_imd_decile))) + 
    geom_area(alpha= 1 , size=0.001, colour="black") +
  # First UK case
  geom_vline(xintercept = as.Date("2020-01-23"), linetype = "33") +
  # First UK lockdown begins
  geom_vline(xintercept = as.Date("2020-03-23"), linetype = "12") +
  # First UK lockdown ends
  geom_vline(xintercept = as.Date("2020-06-01"), linetype = "42") +
  geom_label(aes(as.Date("2020-01-23"), 0, label = "1"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-03-23"), 0, label = "2"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  geom_label(aes(as.Date("2020-06-01"), 0, label = "3"), fill = "white", colour = "grey20", nudge_y = -0.05) +
  scale_x_date(date_breaks = "6 months", date_labels = "%b\n%Y", expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent_format()) +
  scale_fill_brewer(type = "qual", palette = "RdYlBu") + 
  labs(
    title = "Proportion of Calls from different IMD deciles",
    subtitle = "1: First UK Case, 2: Lockdown begins, 3: Lockdown ends",
    x = NULL,
    y = "Proportion",
    fill = "IMD decile"
  ) +
  theme_minimal() +
  theme(legend.position = "bottom") +    guides(fill=guide_legend(nrow=1,byrow=TRUE))

@@

>>>>

cheshire_calls <- calls %>% filter(lsoa %in% unique(cheshire_lsoas$LSOA11NM))
weekly_count_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_count_by_lsoa.csv")
weekly_asb_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_asb_by_lsoa.csv")
weekly_misper_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_misper_by_lsoa.csv")
weekly_violence_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_violence_by_lsoa.csv")
weekly_dv_by_lsoa <- read_csv("/Volumes/n8_covid/weekly_dv_by_lsoa.csv")

call_forecasts <- read_rds("/Volumes/n8_covid/dep_level_forecasts.Rds")

# Note important dates
# Source: https://www.instituteforgovernment.org.uk/sites/default/files/timeline-lockdown-web.pdf
dates <- tribble(
  ~date, ~event,
  "2020-01-31", "first UK COVID case",
  "2020-03-23", "first lockdown begins",
  "2020-06-15", "first lockdown ends",
  "2020-11-05", "second lockdown begins",
  "2020-12-02", "second lockdown ends"
) %>% 
  mutate(
    date = as_date(yearweek(ymd(date))), 
    row = row_number(),
    label = str_glue("{row}. {event}")
  )

forecast_chart <- function (forecasts, types) {

  forecasts %>% 
    filter(dep_level %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y", 
                 limits = as.Date(c("2020-01-06", "2020-12-21"))) +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

}

@@

```{r}
plot_imds <- function(weekly_count_by_lsoa) {

@@

}

plot_imds(weekly_count_by_lsoa)
```

## Check for some different call types

### ASB

plot_imds(weekly_asb_by_lsoa)

@@

### Missing Perons

@@

plot_imds(weekly_misper_by_lsoa)

@@

### Violence/Harassment

plot_imds(weekly_violence_by_lsoa)

### Domestic Incidents

plot_imds(weekly_dv_by_lsoa)

## Forecasts

We see a change for ASB so it might be worth doing a forecast. The number of weekly observations is too low/ noisy if we look at deciles, but can use the IMD rank to break LSOAs into three equal groups: low, medium, and high deprivation.

forecast_chart(call_forecasts, "high")

forecast_chart(call_forecasts, "medium")

forecast_chart(call_forecasts, "low")
